### 2017-10-23 paper/sections/6_results.tex
paper: ken edits
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large slowdowns for
the larger number of creates. For example, ``RPCs" which relies on the internal
CephFS directory structures has a \(90\times\) slowdown for 100K files. It is a
well-known problem that directory data structures do not scale when creating
files in the same directory~\cite{ren:sc2014-indexfs} and any mechanism that
uses these data structures will experience similar slowdowns. Other mechanisms
that write events to a journal ({\it e.g.} the persists, ``Volatile Apply")
experience a much less drastic slowdown because the journal data structure does
not need to be scanned for every operation. Events are written to the end of
the journal without even checking the validity ({\it e.g.}, if the file already
exists for a create), which is another form of relaxed consistency because the
file system assumes the application has resolved conflicting updates in a
different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} ``RPCs" is \(66\times\) slower than ``Volatile
Apply" because sending individual metadata updates over the network is costly.
While ``RPCs" sends a request for every file create, ``Nonvolatile Apply"
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (``Nonvolatile Apply") is \(10\times\) slower.

>>>>

{\it Poorly Scaling Data Structures:} Despite doing the same amount of work,
mechanisms that rely on poorly scaling data structures have large slowdowns for
the larger number of creates. For example, ``RPCs" which relies on the internal
CephFS directory structures has a \(90\times\) slowdown for 100K files. It is a
well-known problem that directory data structures do not scale when creating
files in the same directory~\cite{ren:sc2014-indexfs} and any mechanism that
uses these data structures will experience similar slowdowns. Other mechanisms
that write events to a journal) experience a much less drastic slowdown because
the journal data structure does not need to be scanned for every operation.
Events are written to the end of the journal without even checking the validity
({\it e.g.}, if the file already exists for a create), which is another form of
relaxed consistency because the file system assumes the application has
resolved conflicting updates in a different way.

% RPCs vs. apply: calls to metadata server vs. RADOS
{\it Overhead of RPCs:} ``RPCs" is \(66\times\) slower than ``Volatile
Apply" because sending individual metadata updates over the network is costly.
While ``RPCs" sends a request for every file create, ``Volatile Apply"
writes all the updates to the in-memory journal and applies them to the
in-memory data structures in the metadata server. While communicating the
decoupled namespace directly to the metadata server is faster, communicating
through the object store (``Nonvolatile Apply") is \(10\times\) slower.
